---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# ukpolice

<!-- badges: start -->
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://opensource.org/licenses/MIT)
[![Travis build status](https://travis-ci.org/evanodell/ukpolice.svg?branch=master)](https://travis-ci.org/evanodell/ukpolice)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/evanodell/ukpolice?branch=master&svg=true)](https://ci.appveyor.com/project/evanodell/ukpolice)
[![Coverage status](https://codecov.io/gh/evanodell/ukpolice/branch/master/graph/badge.svg)](https://codecov.io/github/evanodell/ukpolice?branch=master)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/ukpolice)](https://cran.r-project.org/package=ukpolice)
[![GitHub tag](https://img.shields.io/github/tag/evanodell/ukpolice.svg)](https://github.com/evanodell/ukpolice)
[![](https://cranlogs.r-pkg.org/badges/grand-total/ukpolice)](https://cran.r-project.org/package=ukpolice)
[![DOI](https://zenodo.org/badge/178673884.svg)](https://zenodo.org/badge/latestdoi/178673884)
[![R build status](https://github.com/evanodell/ukpolice/workflows/R-CMD-check/badge.svg)](https://github.com/evanodell/ukpolice/actions)
<!-- badges: end -->


The `ukpolice` package downloads data from the UK Police public data API, the full docs of which are available at https://data.police.uk/docs/. Data is available on police forces, crimes, policing areas and stop-and-search.

`ukpolice` is on CRAN, which you can download using:

```{r cran-installation, eval = FALSE}
install.packages("ukpolice")
```

You can install the development version of `ukpolice` from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("evanodell/ukpolice")
```


Data is available on police forces, crimes, policing areas and stop-and-search. All functions begin with `ukc_`.

The example below queries stop and searches by the Thames Valley Police in December 2018, and plots them by police-reported ethnic group.

```{r example, message=FALSE, warning=FALSE}
library(ukpolice)
library(ggplot2)
library(dplyr)

tv_ss <- ukc_stop_search_force("thames-valley", date = "2020-07")

tv_ss2 <- tv_ss %>% 
  filter(!is.na(officer_defined_ethnicity) & outcome != "" ) %>%
  group_by(officer_defined_ethnicity, outcome) %>%
  summarise(n = n()) %>%
  mutate(perc = n/sum(n))

theme_set(theme_bw())

p1 <- ggplot(tv_ss2, aes(x = outcome, y = perc,
                         group = outcome, fill = outcome)) + 
  geom_col(position = "dodge") + 
  scale_y_continuous(labels = scales::percent,
                     breaks = seq(0.25, 0.8, by = 0.25)) + 
  scale_x_discrete(labels = scales::wrap_format(20)) + 
  theme(legend.position = "none",
        axis.text.x = element_text(size = 7, angle = 45, hjust = 1)) + 
  labs(x = "Outcome", 
       y = "Percentage of stop and searches resulting in outcome",
       title = "Stop and Search Outcomes by Police-Reported Ethnicity",
       subtitle = "Thames Valley Police Department, July 2020",
       caption = "(c) Evan Odell | CC-BY-SA") + 
  facet_wrap(~officer_defined_ethnicity)

p1
```

For more details, see the package vignette [vignette](https://docs.evanodell.com/ukpolice/articles/introduction.html) and [function documentation](https://docs.evanodell.com/ukpolice/reference/index.html).

## Meta

Please note that the 'ukpolice' project is released with a [Contributor Code of Conduct](https://github.com/evanodell/ukpolice/blob/master/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.

The UK Police API is operated by the UK Government's Home Office. The `ukpolice` package is not affiliated with the Home Office. All data accessed through `ukpolice` is licenced with [Open Government Licence v3.0](https://www.nationalarchives.gov.uk/doc/open-government-licence/version/3/).

Get citation information for `ukpolice` in R with `citation(package = 'ukpolice')`, or use the citation information below:

Odell E, Tierney N (2020). _ukpolice: Download Data on UK Police and Crime_. doi:
[10.5281/zenodo.2619537](https://doi.org/10.5281/zenodo.2619537), R package version `r packageVersion("ukpolice")`, URL: https://github.com/evanodell/ukpolice.

A BibTeX entry for LaTeX users is:

```
  @Manual{,
    title = {{ukpolice}: Download Data on UK Police and Crime},
    author = {Evan Odell and Nicholas Tierney},
    year = {2020},
    note = {R package version `r packageVersion("ukpolice")`},
    doi = {10.5281/zenodo.2619537},
    url = {https://github.com/evanodell/ukpolice},
  }
```
